\documentclass{article}
\usepackage{graphicx}
%\usepackage{subfig}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{cleveref}
%\usepackage{subfig}	
\usepackage{subcaption}
\usepackage[numbered,framed]{mcode}
\usepackage{fixltx2e}				% For the \textsubscript{} usage
\usepackage{textgreek}				% For greek letters in the normal text (without going to the math mode)


%\usepackage{hyperref} GÖR SÅ ATT \ref{} inte fungerar för eqations och tables

%PREAMBLE
\author{Grupp B}
\title{FRT090 \\GUIDE TO PROGRAM ev3  }				% \\ <=> NEW LINE IN LaTex
\date{November 2014}

\begin{document}
\maketitle	% prints the preamble onto the pdf

\newpage

\begin{itemize}
\item 1.  Boot up option; Choose the "Windows 7 (loader) (on /dev/sda1)" (Please press the down button al the time to actually be fast enough to choose the right boot up option)

\item 2. Choose user. Choose the "frt090\_B" user at login and the old password is valid here as well.

\item 3. Start the ev3 by pressing the middle button. (DO NOT REMOVE THE MICRO- SD card from the ev3 which should bee in at all time). Wait for the sound before proceeding to the next step => ready.


\item 4.  Start eclipse from the desktop. (Choose the default place for workspace)



\item 5. Create a ev3 project. Choose the following options.

\begin{itemize}
	\item  File (at the top left)
	\item New
	\item Project 
	\item Select a wizard pops up, choose the LeJOS EV3 folder and then LeJOS EV3 Project. Click next. State a project name and then press Finish.
\end{itemize}

\item 6. Go to the Package Explorer. Click on the created project. Rightclick on the "scr" and choose new -> Class. Java class pops up, State a name and click finish. 


\item 7. Run a program.
\begin{itemize}
	\item  Right click on the class name
	\item Choose Run as
	\item 2 LeJOS EV3 Program
	\item 
\end{itemize}

\item 7. Seems to be a timed event before the ev3 response.


\end{itemize}




\end{document}