\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Review of the report by Group C}

\author{Group B}

\date{\today}

\begin{document}
\maketitle

\newpage

\section*{Overview of the project and its objectives}

the overview of Group C's report is pretty brief and easy to be followed up but yet can be made some notice on the requirement of some  more detailes and how the actual project work should be done that is to say the theories and methods behind it. 


\section*{Discussion on the modeling needs in the project}

Group C talks very little about the actual modeling. It's clear that they will build the robot with two degrees of freedom, however it's not clear how the actual model that will be controlled will be identified. Which methods will be used to control? Should be specified. If the model is trivial it should be added in the report.


\section*{Description of the models developed so far in the project}

Group C is sufficiently explaining the current progress of the XY coordinate robot. They should, however, specify how the XY robot will be controlled.

\section*{Motivations for the selected modeling and design approaches}

Group C motivates very well why they chose the XY robot and their algorithm strategy.


\section*{Discussion on experiences with respect to modeling and design}

We realize that not much time has gone to work on the project, and that there havn't been much experiences with respect to modeling or design. However, it should be specified whether there were any challenges in the progress so far. Has the time plan been followed etc.

\end{document}